Theories of deliberated choice

### 2023-10-20 simple.tex
Fals

\subsection{Form of theories}
Given an exposure protocol $(I, \allargs, {\allleadsto})$, recall that ${\allleadsto} \in P^{I × \allhist}$.

Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\allleadsto$, thus, $C \subseteq P^{I × \allhist}$.
Given a formula $\psi$, let the corresponding claim be $C_\psi = \set{{\allleadstog} \in P^{I × \allhist} \suchthat {\allleadstog} \text{ satisfies } \psi}$.
A claim is finite iff its cardinal is finite (meaning that it is compatible with a finite number of possibilities).
Let $C^\subseteq = \set{c \subseteq (I × \allhist) × P \suchthat \exists {\allleadstog} \in C \suchthat c \subseteq {\allleadstog}}$ denote the set of non necessarily complete possibilities compatible with $C$ (thus, each element $c \in C^\subseteq$ is right-unique but non necessarily total, meaning that it does not necessarily cover $(I × \allhist)$).
Note that $C^\subseteq$ is downwards closed, meaning that $\forall c \in C^\subseteq: c' \subseteq c \implies c' \in C^\subseteq$.

Given a pair $(I, \allargs)$, an observation $θ \in \Theta$ is a right unique finite subset of $(I × \allhist) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in θ: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
The set $\Theta$ contains the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
Let $S_θ = \set{{\allleadstog} \in P^{I × \allhist} \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
We say that an observation $\theta$ is compatible with a claim $C$ iff $S_\theta \cap C ≠ \emptyset$, equivalently, iff $\theta \in C^\subseteq$.

Given an observation $\theta$, let $\theta^{-1}(P) \subseteq I × \allhist$ denote the pairs $(i, \hist)$ in $\theta$.
Let $\incr(\allhist) = \cup_{N \subseteq \N} \set{A \in (\allhist)^N \suchthat [\card{A_i} = i] \land [i < j \implies A_i \subsetneq A_j]} \subseteq \powerset{\allhist}$ denote the possibly empty embedded sequences of paths.
An element $\theta^{-1}(P)$ can also be seen as a (finite) function associating to each $i \in I$ an element of $\incr(\allhist)$, thus, a possibly empty embedded sequence of elements in $\allhist$.
Therefore, we let $\incr(\allhist)^I = \set{\theta^{-1}(P) \suchthat \theta \in \Theta}$ denote the set of possible observations restricted to $I × \allhist$, the elements of which being called \emph{a priori observation}.
Note that $\incr(\allhist)^I$ is downwards closed, meaning that $\forall O \in \incr(\allhist)^I: O' \subseteq O \implies O' \in \incr(\allhist)^I$.
Let also $\max\incr(\allhist) = \set{A \in \incr(\allhist) \suchthat \nexists A' \in \incr(\allhist) \suchthat A \subset A'} = \set{A \in \incr(\allhist) \cap (\allhist)^\N}$ denote the maximal elements of $\incr(\allhist)$, in the sense of containing sequences that are not a subsequence of another sequence; equivalently, containing those sequences whose sequence of cardinals of their elements equals $\N$.

Let the \emph{simple a priori observations} be defined as $(\allhist)^I$.
Given a simple a priori observation $O: I \mapsto \allhist$, we can define the a priori observation $O_O = \set{(i, \hist) \in I × \allhist \suchthat \forall i \in I: \hist \subseteq O(i)}$ as the completion of $O$ to all sub-paths in $O$.
Given $O$ and ${\allleadstog}$, it follows that $S_{\restr{\allleadstog}{O_O}}$ denotes the “leads to” relations that complete $O_O$ using $\allleadstog$.

@@

\begin{definition}
  We say that $C$ is \emph{syntactically falsifiable}, or just falsifiable, iff
  %$\forall {\allleadstog} \in P^{I × \allhist}: ¬C({\allleadstog}) \implies \exists θ \subseteq {\allleadstog} \suchthat θ \implies ¬C$, meaning that
  $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat S_θ \cap C = \emptyset$.
\end{definition}
Equivalently, iff $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat \theta \notin C^\subseteq$.
Equivalently, $C$ is not falsifiable iff $\exists {\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
\begin{example}
  $(\ar) \ileadstog \phi \lor  (\ar, \ar) \ileadstog \phi \lor …$ is not falsifiable.
  Given any $θ$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in θ} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in θ$, and $l = 1$ otherwise. Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$. We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  \label{ex:unfals}
  $(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi$ is not falsifiable.
  Consider any ${\allleadstog} \notin C$, thus satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
  Consider any $θ \subseteq {\allleadstog}$ and let us prove that $S_θ \cap C ≠ \emptyset$.
  By definition of a general observation, $θ$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $θ$, pick any ${\allleadstog'}$ such that $θ \subset {\allleadstog'} \land t \in {\allleadstog'}$. We have ${\allleadstog'} \in S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  $\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
  Consider any $\allleadstog$ satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$, thus with ${\allleadstog} \notin C$.
  \Cref{ex:unfals} concludes.
\end{example}
\begin{example}
  Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
  Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $θ = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
\end{example}
\begin{example}
  Given an infinite $I$, the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
  Given any ${\allleadstog} \notin C$, thus such that $\forall i: \ar \nileadstostg \phi$, any $θ \subseteq {\allleadstog}$ only has finitely many $(i, \hist, p ≠ \phi)$ thus $S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  Consider any $\ar_1 ≠ \ar_2 \in \allargs$, $p ≠ p' \in P$ and any ${\allleadstog^1}, {\allleadstog^2}$ such that $(\ar_1) \ileadstog^1 p$ and $(\ar_1) \ileadstog^2 p'$.
  The claim $C = \set{{\allleadstog^1}, {\allleadstog^2}}$ is unfalsifiable.

  Consider … (seems redundant).
\end{example}
\begin{remark}
  The claim “For each glass, it will not break on a monday or not break on a tuesday, whatever happens to it.” is not falsifiable. But one can make it stronger and falsify it, by giving a general theory of how glasses break, proving that it holds, and that it is not compatible with the claim. I should think about this.
\end{remark}
\begin{remark}
  To be falsifiable, I need each time I exclude some relation $R$ to also exclude a subset $Cbar$ such that some $O \subseteq R$ satisfies $S_O$ is entirely in $Cbar$.
\end{remark}
\begin{theorem}
  A claim $C$ is falsifiable iff its complement $\Cbar$ satisfies:
  $\forall {\allleadstog} \in \Cbar, \exists \theta \subseteq {\allleadstog} \suchthat S_\theta \subseteq \Cbar$, or equivalently:
  $\forall {\allleadstog} \in \Cbar, \exists O \in (\allhist)^I \suchthat S_{\restr{\allleadstog}{O_O}} \subseteq \Cbar$.
\end{theorem}
\begin{proof}
  The first phrasing follows from the definition of falsifiability.
  Also, the second phrasing implies the first one: pick $\theta = \restr{\allleadstog}{O_O}$.

@@

  To obtain non fals, need to form a relation whose all decompositions into incr associations are in $C$, but itself not in $C$.
\end{remark}
\begin{conjecture}
  Given a claim $C$, consider the subsets of $(\cup_{A \in \max \incr(\allhist)}P^A)^I \cap C^\subseteq$ whose union, considered as a relation on $(I × \allhist) × P$, is total and right-unique (that is, the subsets that form a new relation $\allleadstog$).
  $C$ is falsifiable iff these new elements are necessarily in $C$.
\end{conjecture}
\begin{proof}
  This seems false. (Consider $I = \set{i_1, i_2}$ and $\args = \set{a, b}$ and $\psi$ is ${\ileadsto[i_1]} = {\ileadsto[i_2]}$ and $S = \set{R_1, R_2, …}$ with $R_1$ are all sequences starting with $a$ sent to $p$ and $R_2$ are all sequences starting with $b$ sent to $p' ≠ p$.)
  % Consider $S \subseteq (\cup_{A \in \max \incr(\allhist)}P^A)^I \cap C^\subseteq$ (thus each $R \in S$ is a relation $R \subseteq (I × \allhist) × P$). Assume that $\cup S$ is total and right-unique and is not in $C$.
  % Let us show that $C$ is not falsifiable.
  % Define ${\allleadstog} = \cup S$, pick any $\theta \in \Theta, \theta \subseteq {\allleadstog}$ and let us show that $\theta \in C^\subseteq$.
  % Let us show that $\exists R \in S \suchthat \theta \subseteq R$.
  % Pick any triple $t \in \theta$. Thus, $t \in \cup S$. Thus, for some $R \in S$, $t \in R$. And $R \in C^\subseteq$.
  % Pick any two triples $t, t' \in \theta$. Wlog, $\hist \subseteq \hist'$.
\end{proof}
\begin{theorem}
  Given a claim $C$, consider the sets $S \subseteq C^\subseteq$ such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhist)^I$ and such that $\cup S$, considered as a relation on $(I × \allhist) × P$, is right-unique (that is, $\cup S$ forms a new relation $\allleadstog$).
  $C$ is falsifiable iff all such sets $S$ satisfy $\cup S \in C$.
\end{theorem}
\begin{proof}
  Consider such $S$.
  Assume that $\cup S$ is not in $C$.
  Let us show that $C$ is not falsifiable.
  Define ${\allleadstog} = \cup S$, pick any $\theta \in \Theta, \theta \subseteq {\allleadstog}$ and let us show that $\theta \in C^\subseteq$.
  Define $O \in (\incr(\allhist))^I \suchthat \theta^{-1}(P) \subseteq O$. Thus, $O \in \set{\theta^{-1}(P) \suchthat \theta \in S}$. Pick an element $\theta' \in S \suchthat (\theta')^{-1}(P) = O$. We have $\theta' \in C^\subseteq$ and $\theta^{-1}(P) \subseteq (\theta')^{-1}(P)$.
  Also, $\theta \subseteq \cup S$, and $\cup S$ is right-unique, so $\theta$ coincides with $\theta'$ on its domain (meaning that $\theta = \restr{\theta'}{\theta^{-1}(P)}$). It follows that $\theta \subseteq \theta'$. As $C^\subseteq$ is downwards-closed, this concludes.

  Now, assume that $C$ is not falsifiable and pick any ${\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
  Given any $O \in (\incr(\allhist))^I$, we have $\restr{\allleadstog}{O} \in C^\subseteq$.
  Define $S = \set{\restr{\allleadstog}{O} \suchthat O \in (\incr(\allhist))^I}$.
  The set $S$ satisfies the required conditions and $\cup S = {\allleadstog}$, thus, $\cup S \notin C$.
\end{proof}
Here is another way (perhaps more illuminating) of stating the same thing.
Any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in (\incr(\allhist))^I}$.
Conversely, any set $S$ such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhist)^I$ and $\cup S$ is right-unique corresponds to a unique relation $\cup S = {\allleadstog}$.
Thus, there is a bijection between the set of such sets $S$ and the set of leads to relations.
We can then rephrase the above theorem as follows.
A claim $C$ is falsifiable iff $\forall S \in \mathcal{S}: S \subseteq C^\subseteq \implies \cup S \in C$.
Equivalently, as follows.
\begin{theorem}
  A claim $C$ is falsifiable iff $\forall {\allleadstog} \in P^{I × \allhist}: \set{\restr{\allleadstog}{O} \suchthat O \in (\incr(\allhist))^I} \subseteq C^\subseteq \implies {\allleadstog} \in C$.
\end{theorem}
\begin{proof}
  By definition, $C$ is not falsifiable iff $\exists {\allleadstog} \notin C \suchthat \forall θ \subseteq {\allleadstog}: S_θ \cap C \neq \emptyset$;
  equivalently, iff $\exists {\allleadstog} \notin C \suchthat \forall θ \subseteq {\allleadstog}: θ \in C^\subseteq$;
  equivalently, iff $\exists {\allleadstog} \notin C \suchthat \set{θ \subseteq {\allleadstog}} \subseteq C^\subseteq$.

  The theorem holds because $\forall {\allleadstog} \in P^{I × \allhist}: \set{\restr{\allleadstog}{O} \suchthat O \in (\incr(\allhist))^I} = \set{θ \subseteq {\allleadstog}}$.
\end{proof}

@@

\begin{definition}[Anonymity]
  Given a permutation $\sigma$ over $I$ and any ${\allleadstog} \in P^{I × \allhist}$, let ${\allleadstog} \circ \sigma$ denote $\set{(i, \hist, \phi) \suchthat (\sigma(i), \hist, \phi) \in {\allleadstog}}$ and let $C \circ \sigma$ denote $\set{{\allleadstog} \circ \sigma \suchthat {\allleadstog} \in C}$.
  A claim $C$ is \emph{anonymous} iff $\forall \sigma: C = C \circ \sigma$.
\end{definition}
\begin{example}
  Given $\ar$ and $\phi$, the claim $\ar \ileadstog \phi$ is not anonymous iff $\card{I} ≥ 2$. Indeed, pick any $j ≠ i$ and define $\sigma(i) = j$, $\sigma(j) = i$ and $\forall k \in I \setminus \set{i, j}: \sigma(k) = k$, then $C = \set{{\allleadstog} \suchthat {\allleadstog}(i, \ar) = \phi}$, which contains in particular ${\allleadsto}$ defined as $\forall \hist: [\forall k \in I \setminus \set{j}, {\allleadsto}(k, \hist) = \phi \land {\allleadsto}(j, \hist) = ¬\phi$; while $C \circ \sigma = \set{{\allleadstog} \suchthat {\allleadstog}(j, \ar) = \phi}$ which does not contain ${\allleadsto}$.
\end{example}

>>>>

\subsection{Form of theories}
Given an exposure protocol $(I, \allargs, {\allleadsto})$, recall that ${\allleadsto} \in \allallleadsto$.

Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\allleadsto$, thus, $C \subseteq \allallleadsto$.
Given a formula $\psi$, let the corresponding claim be $C_\psi = \set{{\allleadstog} \in \allallleadsto \suchthat {\allleadstog} \text{ satisfies } \psi}$.
A claim is finite iff its cardinal is finite (meaning that it is compatible with a finite number of possibilities).
Let $C^\subseteq = \set{c \subseteq (I × \allhist) × P \suchthat \exists {\allleadstog} \in C \suchthat c \subseteq {\allleadstog}}$ denote the set of non necessarily complete possibilities compatible with $C$ (thus, each element $c \in C^\subseteq$ is right-unique but non necessarily total, meaning that it does not necessarily cover $(I × \allhist)$).
Note that $C^\subseteq$ is downwards closed, meaning that $\forall c \in C^\subseteq: c' \subseteq c \implies c' \in C^\subseteq$.

Given a pair $(I, \allargs)$, an observation $θ \in \Theta$ is a right unique finite subset of $(I × \allhist) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in θ: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
The set $\Theta$ contains the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
Let $S_θ = \set{{\allleadstog} \in \allallleadsto \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.
We say that an observation $\theta$ is compatible with a claim $C$ iff $S_\theta \cap C ≠ \emptyset$, equivalently, iff $\theta \in C^\subseteq$.

Given an observation $\theta$, let $\theta^{-1}(P) \subseteq I × \allhist$ denote the pairs $(i, \hist)$ in $\theta$.
Let $\incr(\allhist) = \set{\emptyset} \cup \cup_{\emptyset \neq N \subseteq \N} \set{A(N) \suchthat A \in (\allhist)^N \land [\card{A_i} = i] \land [i < j \implies A_i \subsetneq A_j]} \subseteq \powerset{\allhist}$ denote the possibly empty embedded sequences of paths.
An element $\theta^{-1}(P)$ can also be seen as a (finite) function associating to each $i \in I$ an element of $\incr(\allhist)$.
Therefore, we let $\finite(\incr(\allhist)^I) = \set{\theta^{-1}(P) \suchthat \theta \in \Theta}$ denote the set of possible observations restricted to $I × \allhist$, the elements of which being called \emph{a priori observation}, where $\finite(\incr(\allhist)^I)$ denote the functions $f: I \mapsto \incr(\allhist)$ with finite support, thus $\card{f^{-1}(\incr(\allhist) \setminus \emptyset)} < \N$.
Note that $\finite(\incr(\allhist)^I)$ and $\incr(\allhist)^I$ are downwards closed, meaning that $\forall O \in \finite(\incr(\allhist)^I): O' \subseteq O \implies O' \in \finite(\incr(\allhist)^I)$ and $\forall O \in \incr(\allhist)^I: O' \subseteq O \implies O' \in \incr(\allhist)^I$.
Let also $\max\incr(\allhist) = \set{A \in \incr(\allhist) \suchthat \nexists A' \in \incr(\allhist) \suchthat A \subset A'} = \set{A \in \incr(\allhist) \cap (\allhist)^\N}$ denote the maximal elements of $\incr(\allhist)$, in the sense of containing sequences that are not a subsequence of another sequence; equivalently, containing those sequences whose sequence of cardinals of their elements equals $\N$.

Let the \emph{simple a priori observations} be defined as $\cup_{J \subseteq_\finite I} (\allhist)^J$, equivalently, as the right-unique finite relations over $I × \allhist$.
Given a simple a priori observation $O: J \mapsto \allhist$, we can define the a priori observation $O_O = \set{(i, \hist) \in J × \allhist \suchthat \forall i \in J: \hist \subseteq O(i)}$ as the completion of $O$ to all sub-paths in $O$.
Given $O$ and ${\allleadstog}$, it follows that $S_{\restr{\allleadstog}{O_O}}$ denotes the “leads to” relations that complete $O_O$ using $\allleadstog$.

@@

\begin{definition}
  We say that $C$ is \emph{syntactically falsifiable}, or just falsifiable, iff
  %$\forall {\allleadstog} \in \allallleadsto: ¬C({\allleadstog}) \implies \exists θ \subseteq {\allleadstog} \suchthat θ \implies ¬C$, meaning that
  $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat S_θ \cap C = \emptyset$.
\end{definition}
Equivalently, iff $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat \theta \notin C^\subseteq$.
Equivalently, $C$ is not falsifiable iff $\exists {\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
\begin{example}
  $(\ar) \ileadstog \phi \lor  (\ar, \ar) \ileadstog \phi \lor …$ is not falsifiable.
  Given any $θ$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in θ} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in θ$, and $l = 1$ otherwise. Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$. We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  \label{ex:unfals}
  $(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi$ is not falsifiable.
  Consider any ${\allleadstog} \notin C$, thus satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
  Consider any $θ \subseteq {\allleadstog}$ and let us prove that $S_θ \cap C ≠ \emptyset$.
  By definition of a general observation, $θ$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $θ$, pick any ${\allleadstog'}$ such that $θ \subset {\allleadstog'} \land t \in {\allleadstog'}$. We have ${\allleadstog'} \in S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  $\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
  Consider any $\allleadstog$ satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$, thus with ${\allleadstog} \notin C$.
  \Cref{ex:unfals} concludes.
\end{example}
\begin{example}
  Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
  Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $θ = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
\end{example}
\begin{example}
  Given an infinite $I$, the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
  Given any ${\allleadstog} \notin C$, thus such that $\forall i: \ar \nileadstostg \phi$, any $θ \subseteq {\allleadstog}$ only has finitely many $(i, \hist, p ≠ \phi)$ thus $S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  Consider any $\ar_1 ≠ \ar_2 \in \allargs$, $p ≠ p' \in P$ and any ${\allleadstog^1}, {\allleadstog^2}$ such that $(\ar_1) \ileadstog^1 p$ and $(\ar_1) \ileadstog^2 p'$.
  The claim $C = \set{{\allleadstog^1}, {\allleadstog^2}}$ is unfalsifiable.

  Consider … (seems redundant).
\end{example}
\begin{remark}
  The claim “For each glass, it will not break on a monday or not break on a tuesday, whatever happens to it.” is not falsifiable. But one can make it stronger and falsify it, by giving a general theory of how glasses break, proving that it holds, and that it is not compatible with the claim. I should think about this.
\end{remark}
\begin{remark}
  To be falsifiable, I need each time I exclude some relation $R$ to also exclude a subset $Cbar$ such that some $O \subseteq R$ satisfies $S_O$ is entirely in $Cbar$.
\end{remark}
\begin{theorem}
  A claim $C$ is falsifiable iff its complement $\Cbar = \allallleadsto \setminus C$ satisfies:
  $\forall {\allleadstog} \in \Cbar, \exists \theta \subseteq {\allleadstog} \suchthat S_\theta \subseteq \Cbar$, or equivalently:
  $\forall {\allleadstog} \in \Cbar, \exists O \in (\allhist)^I \suchthat S_{\restr{\allleadstog}{O_O}} \subseteq \Cbar$.
\end{theorem}
\begin{proof}
  The first phrasing follows from the definition of falsifiability.
  Also, the second phrasing implies the first one: pick $\theta = \restr{\allleadstog}{O_O}$.

@@

  To obtain non fals, need to form a relation whose all decompositions into incr associations are in $C$, but itself not in $C$.
\end{remark}
\begin{conjecture}
  Given a claim $C$, consider the subsets of $(\cup_{A \in \max \incr(\allhist)}P^A)^I \cap C^\subseteq$ whose union, considered as a relation on $(I × \allhist) × P$, is total and right-unique (that is, the subsets that form a new relation $\allleadstog$).
  $C$ is falsifiable iff these new elements are necessarily in $C$.
\end{conjecture}
\begin{proof}
  This seems false. (Consider $I = \set{i_1, i_2}$ and $\args = \set{a, b}$ and $\psi$ is ${\ileadsto[i_1]} = {\ileadsto[i_2]}$ and $S = \set{R_1, R_2, …}$ with $R_1$ are all sequences starting with $a$ sent to $p$ and $R_2$ are all sequences starting with $b$ sent to $p' ≠ p$.)
  % Consider $S \subseteq (\cup_{A \in \max \incr(\allhist)}P^A)^I \cap C^\subseteq$ (thus each $R \in S$ is a relation $R \subseteq (I × \allhist) × P$). Assume that $\cup S$ is total and right-unique and is not in $C$.
  % Let us show that $C$ is not falsifiable.
  % Define ${\allleadstog} = \cup S$, pick any $\theta \in \Theta, \theta \subseteq {\allleadstog}$ and let us show that $\theta \in C^\subseteq$.
  % Let us show that $\exists R \in S \suchthat \theta \subseteq R$.
  % Pick any triple $t \in \theta$. Thus, $t \in \cup S$. Thus, for some $R \in S$, $t \in R$. And $R \in C^\subseteq$.
  % Pick any two triples $t, t' \in \theta$. Wlog, $\hist \subseteq \hist'$.
\end{proof}
\begin{theorem}[To check considering finiteness of observations]
  Given a claim $C$, consider the sets $S \subseteq C^\subseteq$ such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhist)^I$ and such that $\cup S$, considered as a relation on $(I × \allhist) × P$, is right-unique (that is, $\cup S$ forms a new relation $\allleadstog$).
  $C$ is falsifiable iff all such sets $S$ satisfy $\cup S \in C$.
\end{theorem}
\begin{proof}
  Consider such $S$.
  Assume that $\cup S$ is not in $C$.
  Let us show that $C$ is not falsifiable.
  Define ${\allleadstog} = \cup S$, pick any $\theta \in \Theta, \theta \subseteq {\allleadstog}$ and let us show that $\theta \in C^\subseteq$.
  Define $O \in (\incr(\allhist))^I \suchthat \theta^{-1}(P) \subseteq O$. Thus, $O \in \set{\theta^{-1}(P) \suchthat \theta \in S}$. Pick an element $\theta' \in S \suchthat (\theta')^{-1}(P) = O$. We have $\theta' \in C^\subseteq$ and $\theta^{-1}(P) \subseteq (\theta')^{-1}(P)$.
  Also, $\theta \subseteq \cup S$, and $\cup S$ is right-unique, so $\theta$ coincides with $\theta'$ on its domain (meaning that $\theta = \restr{\theta'}{\theta^{-1}(P)}$). It follows that $\theta \subseteq \theta'$. As $C^\subseteq$ is downwards-closed, this concludes.

  Now, assume that $C$ is not falsifiable and pick any ${\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
  Given any $O \in (\incr(\allhist))^I$, we have $\restr{\allleadstog}{O} \in C^\subseteq$.
  Define $S = \set{\restr{\allleadstog}{O} \suchthat O \in (\incr(\allhist))^I}$.
  The set $S$ satisfies the required conditions and $\cup S = {\allleadstog}$, thus, $\cup S \notin C$.
\end{proof}
Here is another way (perhaps more illuminating) of stating the same thing.
\begin{remark}
  Any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in (\finite(\incr(\allhist))^I)}$.
  (Also, any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in \cup_{J \subseteq_\finite I} (\allhist)^J}$.)
  Conversely, any set $S$ of observations such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhist)^I$ and $\cup S$ is right-unique corresponds to a unique relation $\cup S = {\allleadstog}$.
  Thus, there is a bijection between the set $\mathcal{S}$ of such sets $S$ and the set of leads to relations.

  Therefore,
  a claim $C$ is falsifiable iff $\forall S \in \mathcal{S}: S \subseteq C^\subseteq \implies \cup S \in C$.
\end{remark}

\begin{theorem}
  A claim $C$ is falsifiable iff \[\forall f \in C^{\finite(\incr(\allhist)^I)}: \cup_{O \in \finite(\incr(\allhist)^I)} \restr{f(O)}{O} \in C.\]
\end{theorem}
\begin{proof}
  By definition, $C$ is not falsifiable iff $\exists {\allleadstog} \notin C \suchthat \forall θ \subseteq {\allleadstog}: S_θ \cap C \neq \emptyset$;
  equivalently, iff $\exists {\allleadstog} \notin C \suchthat \forall θ \subseteq {\allleadstog}: θ \in C^\subseteq$;
  equivalently, iff $\exists {\allleadstog} \notin C \suchthat \set{θ \subseteq {\allleadstog}} \subseteq C^\subseteq$.

  The theorem states that a claim $C$ is falsifiable iff $\forall {\allleadstog} \in \allallleadsto: \set{\restr{\allleadstog}{O} \suchthat O \in \finite(\incr(\allhist)^I)} \subseteq C^\subseteq \implies {\allleadstog} \in C$.

  This holds because $\forall {\allleadstog} \in \allallleadsto: \set{\restr{\allleadstog}{O} \suchthat O \in \finite(\incr(\allhist)^I)} = \set{θ \subseteq {\allleadstog}}$.
\end{proof}

@@

\begin{definition}[Anonymity]
  Given a permutation $\sigma$ over $I$ and any ${\allleadstog} \in \allallleadsto$, let ${\allleadstog} \circ \sigma$ denote $\set{(i, \hist, \phi) \suchthat (\sigma(i), \hist, \phi) \in {\allleadstog}}$ and let $C \circ \sigma$ denote $\set{{\allleadstog} \circ \sigma \suchthat {\allleadstog} \in C}$.
  A claim $C$ is \emph{anonymous} iff $\forall \sigma: C = C \circ \sigma$.
\end{definition}
\begin{example}
  Given $\ar$ and $\phi$, the claim $\ar \ileadstog \phi$ is not anonymous iff $\card{I} ≥ 2$. Indeed, pick any $j ≠ i$ and define $\sigma(i) = j$, $\sigma(j) = i$ and $\forall k \in I \setminus \set{i, j}: \sigma(k) = k$, then $C = \set{{\allleadstog} \suchthat {\allleadstog}(i, \ar) = \phi}$, which contains in particular ${\allleadsto}$ defined as $\forall \hist: [\forall k \in I \setminus \set{j}, {\allleadsto}(k, \hist) = \phi \land {\allleadsto}(j, \hist) = ¬\phi$; while $C \circ \sigma = \set{{\allleadstog} \suchthat {\allleadstog}(j, \ar) = \phi}$ which does not contain ${\allleadsto}$.
\end{example}
